---
title: "Flourish Example"
author: "Kelly Bodwin and Visruth Srimath Kandali"
format: html
embed-resources: true
filters:
    - flourish
---

This filter adds the ability to specify in hashpipe comments instructions for highlighting the code in the rendered chunk.

See `talk.qmd` and `talk.html` in this repository for RevealJS slides featuring `flourish`

## How to `flourish`

By default, ordinary yellow highlighting is used:

```yaml
#| flourish:
#| - target-rx: "[0-9]*"
```

```{r}
#| flourish:
#| - target-rx: "[0-9]*"

x <- 1:10
mean(x = 1:10)
```

It is also possible to specify custom formatting with the `style` tag. Here you must provide the exact text that would appear in a CSS class definition.

```yaml
#| flourish:
#| - target:
#|      - "mean"
#|      - style:
#|            - "background-color: #FFC0CB;"
```

```{r}
#| flourish:
#| - target:
#|      - "mean"
#|      - style:
#|            - "background-color: #FFC0CB;"

x <- 1:10
mean(x = 1:10)
```

## Blanking Code Using `flourish`

One fun way to use this is to blank out code pieces for student exercises.

```yaml
#| flourish:
#| - target:
#|     - "mean"
#|     - style: 
#|         - "color: transparent;"
```

```{r}
#| flourish:
#| - target:
#|     - "mean"
#|     - style:
#|         - "color: transparent;"
#|         - "text-decoration: underline;"

x <- 1:10
mean(x = 1:10)
```

Note that blanking out pieces with `style` means the answers are still visible in the underlying HTML.  To fully replace the answers with placeholder space, use `mask`:

```yaml
#| flourish:
#| - target:
#|     - "mean"
#|     - mask: true
#|     - style: "text-decoration: underline;"
```

```{r}
#| flourish:
#| - target:
#|     - "mean"
#|     - mask: true
#|     - style: "text-decoration: underline;"

x <- 1:10
mean(x = 1:10)
```

## Comprehensive Example

This example seeks to serve as a reference for all your `flourish` needs.

```{.yaml}
#| flourish:
#| - target: "mean"
#| - target:
#|     - "sd"
#|     - mask: true
#|     - style: "text-decoration: underline;"
#| - target-rx: "[0-9]*"
#| - target:
#|      - "x"
#|      - style: "font-weight: bold;"
#| - target:
#|      - "set.seed"
#|      - "rnorm"
#|      - style:
#|            - "font-style: italic;"
#|            - "background-color: #468e5d;"
```
```{r}
#| flourish:
#| - target:
#|     - "*"
#|     - "<-"
#|     - "|>"
#| - target:
#|     - "sd"
#|     - mask: true
#|     - style: "text-decoration: underline;"
#| - target-rx: "[0-9]*"
#| - target:
#|     - "mean"
#|     - "x"
#|     - style: "font-weight: bold;"
#| - target:
#|     - "set.seed"
#|     - "rnorm"
#|     - style:
#|           - "font-style: italic;"
#|           - "background-color: #468e5d;"
set.seed(0)
x <- rnorm(10)
x * 10 |> median()
mean(x)
sd(x)
```

## Fun With CSS

Note that `flourish` admits (almost) any valid CSS, which allows us to do stuff like this: 

```yaml
#| flourish:
#| - target:
#|      - "wackyyy"
#|      - style:
#|            - "background-color: #bd8c51;"
#|            - "text-decoration: line-through;"
#|            - "-webkit-text-stroke: 1px black;"
#|            - "filter: blur(1px);"
#|            - "font-family: 'Brush Script MT', cursive;"
```

```{r}
#| flourish:
#| - target:
#|      - "wackyyy"
#|      - style:
#|            - "background-color: #bd8c51;"
#|            - "text-decoration: line-through;"
#|            - "-webkit-text-stroke: 1px black;"
#|            - "filter: blur(1px);"
#|            - "font-family: 'Brush Script MT', cursive;"

wackyyy <- 1:10
mean(wackyyy)
```

With limited testing, animations don't seem to work.
